### 2019-03-06 micro4_1.tex
Micro

The definition of the world $arbitrary$ is the following:

@@

>>>>

The definition of the term $arbitrary$ is the following:

@@

Suppose access to a university education becomes less dependent on wealth or social class.
Using a signalling model of education, what predictions would you make about how wage
inequality within age cohorts would change?

There can be three types of predictions: wage inequality can increase, decrease or remains unchanged. And in principle all three types can be possible, depending on parameters of the model and concept of equilibrium we use (PBE or PBE+intuitive criterion refinement)

Assume for simplicity that we have only two types of workers (of high productivity and of low productivity) and that education is useless, in the sense that it does not increase productivity (a plausible assumption for Russian educational system).

In addition assume that we have a separating equilibrium i.e. the wage inequality is $\theta_H - \theta_L$ and moreover let us use the intuitive criterion refinement which eliminates all pooling equilibria. Since indifference curves of low type workers become flatter, it is now becomes profitable for them to deviate and to pretend to be workers of high productivity. In this case either firms become unable to distinguish between the types and offer a single wage for all types (pooling equilibrium) and as a result, inequality decreases to 0, or workers of high type just increase their level of education (starting to pursue PhD for example) and firm still are able to distinguish between types and offer different wages, hence the wage inequality remains unchanged.
